---
title: "draw_different_lipid_alongLines"
output: rmarkdown::html_vignette
number_sections: true
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
vignette: >
  %\VignetteIndexEntry{draw_different_lipid_alongLines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=7, fig.height=5,
  fig.align = "center"
)
```


I frequently use the `grid` and `purrr` package, so besides load the `PathwayIlluminator`, these two packages are needed.

```{r setup}
library(PathwayIlluminator)
library(grid)
library(purrr)
## new packages need to added
library(gridBezier)
```

## Get the supported single phospholipid model

The basic model makes up the whole bi-layer lipids , so , at first we take a look at the supported single phospholipid model.

```{r singlePhospholipidModel,fig.width=4,fig.height=3}
show_phospholipid_models()
```

## draw open shape bilayer lipids along the curve

### horizontal line 

```{r horizontalLine,fig.height=6}
w_and_h <- par('din')
x <- seq(from = 1, to = w_and_h[1] - 1, length.out = 35)
# the simplest form of the line
#
grid.newpage()
for (ii in 1:6) {
  y <- rep(ii,length(x))
  painter <- create_lipidBilayer_drawer(ii)
  painter$draw_lipid_along_curve(lineX = x, lineY = y - 0.5)
}
```


### Power function curve

```{r ,fig.height=3}
w_and_h <- par('din')
x <- seq(from = 1, to = w_and_h[1] - 1, length.out = 35)
# the simplest form of the line
y <- x ^ (1 /3) + 0.5
grid.newpage()
painter <- create_lipidBilayer_drawer(1,draw_circle_head = T)
painter$current_lipid_model <- lipid_models[[1]];
painter$draw_lipid_along_curve(lineX = x, lineY = y)

```


### Draw the curve of the quadratic equation

```{r}
w_and_h <- par('din')
x <- seq(from = 1, to = w_and_h[1] - 1, length.out = 40)
# the simplest form of the line
y <- - 0.5 * (x - 3) ^ 2 + 4
grid.newpage()
grid.lines(x,y,default.units = 'in')

painter <- create_lipidBilayer_drawer(1,draw_circle_head = F)
painter$current_lipid_model <- lipid_models[[1]];
painter$draw_lipid_along_curve(lineX = x, lineY = y)
```


### bezier curve

```{r}
# Use bezier function to get the curve ------------------------------------
w_and_h <- par('din')
centerLocation <- 0.5 * w_and_h
moveX <- centerLocation[1]; moveY <- centerLocation[2]


grid.newpage()

vertical_up_length <- 1;

leaf_point <- create_point(1, moveY);
right_point <- create_point(w_and_h[1] - 1, moveY)
top_left_point <- create_point(moveX *0.5, moveY + vertical_up_length)
top_right_point <- create_point(moveX * 1.5, moveY + vertical_up_length)

bGrob <- BezierGrob(
  x = c(leaf_point@x, top_left_point@x, top_right_point@x, right_point@x),
  y =c(leaf_point@y, top_left_point@y, top_right_point@y, right_point@y),
  default.units = 'in',
  stepFn = function(...)
    seq(0, 1, length.out = 35)
)
pts <- BezierPoints(bGrob)
x <- pts$x
y <- pts$y
painter <- create_lipidBilayer_drawer(draw_circle_head = F)
grid.newpage()
painter$draw_lipid_along_curve(x,y)
```

### sin function based curve

we can take a look of different single phospholipid models

```{r ,fig.height= 9}
# Sin and cos -------------------------------------------------------------
w_and_h <- par('din')

x <- seq(from = 1, to = w_and_h[1] - 1, length.out = 40)
y <- sin(x) + 1.5
grid.newpage()
painter <- create_lipidBilayer_drawer(lipidModelIndex = 3,draw_circle_head = T)
painter$draw_lipid_along_curve(lineX = x, lineY = y)

y <- sin(x) + 2.5
painter <- create_lipidBilayer_drawer(3,draw_circle_head = F)
painter$draw_lipid_along_curve(lineX = x, lineY = y)

y <- sin(x) + 3.5
painter <- create_lipidBilayer_drawer(3,draw_circle_head = T)
painter$draw_lipid_along_curve(lineX = x, lineY = y)

y <- sin(x) + 4.5
painter <- create_lipidBilayer_drawer(4,draw_circle_head = T)
painter$draw_lipid_along_curve(lineX = x, lineY = y)

y <- sin(x) + 5.5
painter <- create_lipidBilayer_drawer(1,draw_circle_head = T)
painter$draw_lipid_along_curve(lineX = x, lineY = y)

y <- sin(x) + 6.5
painter <- create_lipidBilayer_drawer(6,draw_circle_head = T)
painter$draw_lipid_along_curve(lineX = x, lineY = y)

y <- sin(x) + 7.5
painter <- create_lipidBilayer_drawer(6,draw_circle_head = F)
painter$draw_lipid_along_curve(lineX = x, lineY = y)
```

Which one do you prefer? there are two parameters that can be used together to produce different effects, namely `draw_circle_head` and `lipidModelIndex` .

## draw closed shape bilayer lipids along the curve

For the circle and rectangle, they are the closed shape (or called polygon).

### circular shape

```{r}
produce_circle_lipid <- function(from = 0, to = 365){
  df_round <- produce_model_coordinate_points(from = from,to = to,radius = 2) + 2.5
  x <- df_round[1,] + 1
  y <- df_round[2,]
  # y <- x
  grid.newpage()
  painter <- create_lipidBilayer_drawer()
  painter$draw_circle_head <- T
  painter$current_lipid_model <- lipid_models[[1]];
  painter$draw_lipid_along_curve(lineX = x, lineY = y)
}
produce_circle_lipid()
```

### The rectangle shape

Firstly, let us get a showcase.

```{r ,fig.height= 5.8}
show_roundRect_biLayer()
```

If you generate the polygon DIY.

```{r fig.height=4,fig.width= 5}
painter <- create_lipidBilayer_drawer(draw_circle_head = T)
painter$lipid_head_par <- gpar(fill = 'lightblue', col = 'blue4')
painter$draw_only_upLayer <- T

coords <- create_round_rectangle_xyCoords(x = 1, y = 0.5, w = 3, h = 3, r = 1, space = 0.1)

grid.newpage()
painter$draw_only_upLayer <- F
painter$draw_lipid_along_curve(lineX = coords[1, ],  lineY = coords[2, ])
grid.polygon(x = coords[1, ],
             y = coords[2, ],
             default.units = 'in', gp = gpar(fill = NA))
```


you need to specify the `closedPolygon = T` argument in the method `draw_lipid_along_curve()`.

```{r fig.height=4,fig.width= 5}
painter <- create_lipidBilayer_drawer(draw_circle_head = T)
painter$lipid_head_par <- gpar(fill = 'lightblue', col = 'blue4')
painter$draw_only_upLayer <- T

coords <- create_round_rectangle_xyCoords(x = 1, y = 0.5, w = 3, h = 3, r = 1, space = 0.1)

grid.newpage()
painter$draw_only_upLayer <- F
painter$draw_lipid_along_curve(lineX = coords[1, ],  lineY = coords[2, ] , closedPolygon = T)
grid.polygon(x = coords[1, ],
             y = coords[2, ],
             default.units = 'in', gp = gpar(fill = NA))
```


## How about draw the one layer lipid

This feature also supported.

```{r fig.height=2}
w_and_h <- par('din')
x <- seq(from = 1, to = w_and_h[1] - 1, length.out = 40)
y <- rep(1,length(x))

painter <- create_lipidBilayer_drawer(draw_circle_head = T)
painter$lipid_head_par <- gpar(fill = 'lightblue', col = 'blue4')
painter$draw_only_upLayer <- T

grid.newpage()
painter$draw_lipid_along_curve(lineX = x,  lineY = y)

grid.circle(x,y,default.units = 'in', r = unit(1,'pt'))

grid.newpage()
painter$draw_lipid_along_curve(lineX = rev(x),  lineY = y)
grid.circle(x = rev(x),  y = y , r = unit(1,'pt'),default.units = 'in')
```


How about the vertical line.

```{r fig.height=3,fig.width=3}
w_and_h <- par('din')
y <- seq(from = 0.3, to = w_and_h[2] - 0.3, by = 0.15)
x <- rep(2,length(y))

grid.newpage()
painter$draw_lipid_along_curve(lineX = x,  lineY = y)

grid.circle(x,y,default.units = 'in', r = unit(1,'pt'))

grid.newpage()
painter$draw_lipid_along_curve(lineX = x,  lineY = rev(y))
grid.circle(x = x,  y = rev(y) , r = unit(1,'pt'),default.units = 'in')
```


# How to change the color?


```{r ,fig.height=3}
w_and_h <- par('din')
x <- seq(from = 1, to = w_and_h[1] - 1, length.out = 35)
# the simplest form of the line
y <- x ^ (1 /3) + 0.5
grid.newpage()
painter <- create_lipidBilayer_drawer(1,draw_circle_head = T)
painter$lipid_head_par <- gpar(fill = '#F7EDD4' , col = '#AC9875')
painter$lipid_line_par <- gpar(col = '#BFB49D',lwd = 2) 
painter$current_lipid_model <- lipid_models[[1]];
painter$draw_lipid_along_curve(lineX = x, lineY = y)
```

We can change the `lipid_head_par` and `lipid_line_par` parameters to make customized appearance.
