---
title: "draw_PPAR_pathway"
output: rmarkdown::html_vignette
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
vignette: >
  %\VignetteIndexEntry{draw_PPAR_pathway}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8, fig.height=5,
  fig.align = "center"
)
```

So, let us take a journey to draw a figure of the real world knowledge. This time, we choose the PPAR pathway as an example.

```{r setup}
library(PathwayIlluminator)
library(grid)
```

# The drawing process step by step

Overall, we draw the pathway through 1) Cell membrane and nuclear membrane, 2) Node of complex or single protein, 3) DNA string 4) edge of the direction or regulation.

## First, cell membrane and nuclear membrane

```{r}
grid.newpage()

show_grid_forAssistance()

df_lipidsPoints <-
  produce_model_coordinate_points(
    from = -180 ,
    to = 70,
    by = 3,
    radius = 3.5
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5, moveY = 2)

drawer <-
  create_lipidBilayer_drawer(lipidModelIndex = 6, draw_circle_head = T)
drawer$draw_lipid_along_curve(lineX = df_lipidsPoints[1,] , lineY = df_lipidsPoints[2,])

df_nucleus_membrane <-
  produce_model_coordinate_points(
    from = 0,
    to = 360,
    by = 2,
    radius = 2
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5.5, moveY = 1.5)

# drawer <-
#   create_lipidBilayer_drawer(lipidModelIndex = 4, draw_circle_head = T)
# drawer$desired_height <- 0.1
#
#
# startPos <- seq(from = 1, by = 6, to = ncol(df_nucleus_membrane) - 10)
# walk(startPos, .f = function(s){
#   columns <- s:(s+5);
#   drawer$draw_lipid_along_curve(lineX = df_nucleus_membrane[1,columns] , lineY = df_nucleus_membrane[2,columns])
# })
painter2 <- create_roundRectBilayer_drawer(numberOfIntervals = 10)
painter2$desired_height <- 0.08
painter2$draw_along_curve(lineX = df_nucleus_membrane[1,], lineY = df_nucleus_membrane[2,])

```

Note: we use the `show_grid_forAssistance()` function to produce the grid dash lines to determine the location of the staffs.

## Next, DNA string

```{r}
grid.newpage()

show_grid_forAssistance()

df_lipidsPoints <-
  produce_model_coordinate_points(
    from = -180 ,
    to = 70,
    by = 3,
    radius = 3.5
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5, moveY = 2)

drawer <-
  create_lipidBilayer_drawer(lipidModelIndex = 6, draw_circle_head = T)
drawer$draw_lipid_along_curve(lineX = df_lipidsPoints[1,] , lineY = df_lipidsPoints[2,])

df_nucleus_membrane <-
  produce_model_coordinate_points(
    from = 0,
    to = 360,
    by = 2,
    radius = 2
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5.5, moveY = 1.5)

# drawer <-
#   create_lipidBilayer_drawer(lipidModelIndex = 4, draw_circle_head = T)
# drawer$desired_height <- 0.1
#
#
# startPos <- seq(from = 1, by = 6, to = ncol(df_nucleus_membrane) - 10)
# walk(startPos, .f = function(s){
#   columns <- s:(s+5);
#   drawer$draw_lipid_along_curve(lineX = df_nucleus_membrane[1,columns] , lineY = df_nucleus_membrane[2,columns])
# })
painter2 <- create_roundRectBilayer_drawer(numberOfIntervals = 10)
painter2$desired_height <- 0.08
painter2$draw_along_curve(lineX = df_nucleus_membrane[1,], lineY = df_nucleus_membrane[2,])



drawer_NDA <- create_DNA_drawer(dnaType = 2,numOfRepeats = 3,desired_height = 0.35)
drawer_NDA$draw_me(3.6,1)


transcriptMachine1 <-
  create_round_rectangular_node(width = 0.5,
                                height = 0.4,
                                inner_extension_ratio = 0.2)
transcriptMachine1$label <- NA
transcriptMachine1$xAxis_or_radius <- 4.3
transcriptMachine1$yAxis_or_angle <- 1.45
transcriptMachine1$circle_radius <- 1
transcriptMachine1$text_position <- c(0.5, 0.5)
transcriptMachine1$draw_me()


```

## Draw node of complex or single protein

```{r}
grid.newpage()

show_grid_forAssistance()

df_lipidsPoints <-
  produce_model_coordinate_points(
    from = -180 ,
    to = 70,
    by = 3,
    radius = 3.5
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5, moveY = 2)

drawer <-
  create_lipidBilayer_drawer(lipidModelIndex = 6, draw_circle_head = T)
drawer$draw_lipid_along_curve(lineX = df_lipidsPoints[1,] , lineY = df_lipidsPoints[2,])

df_nucleus_membrane <-
  produce_model_coordinate_points(
    from = 0,
    to = 360,
    by = 2,
    radius = 2
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5.5, moveY = 1.5)

# drawer <-
#   create_lipidBilayer_drawer(lipidModelIndex = 4, draw_circle_head = T)
# drawer$desired_height <- 0.1
#
#
# startPos <- seq(from = 1, by = 6, to = ncol(df_nucleus_membrane) - 10)
# walk(startPos, .f = function(s){
#   columns <- s:(s+5);
#   drawer$draw_lipid_along_curve(lineX = df_nucleus_membrane[1,columns] , lineY = df_nucleus_membrane[2,columns])
# })
painter2 <- create_roundRectBilayer_drawer(numberOfIntervals = 10)
painter2$desired_height <- 0.08
painter2$draw_along_curve(lineX = df_nucleus_membrane[1,], lineY = df_nucleus_membrane[2,])



drawer_NDA <- create_DNA_drawer(dnaType = 2,numOfRepeats = 3,desired_height = 0.35)
drawer_NDA$draw_me(3.6,1)




Lipoxygenases_receptor <-
  create_round_rectangular_node(width = 0.4,
                                height = 0.6,
                                inner_extension_ratio = 0.2)
Lipoxygenases_receptor$label <- 'Lipoxygenases'
Lipoxygenases_receptor$xAxis_or_radius <- 5
Lipoxygenases_receptor$yAxis_or_angle <- 4
Lipoxygenases_receptor$circle_radius <- 2
Lipoxygenases_receptor$text_position <- c(0.5, 1.1)
Lipoxygenases_receptor$draw_me()




ppar_a_receptor <-
  create_oval_node(scaleHeight = 0.8)
ppar_a_receptor$label <- 'PPARa'
ppar_a_receptor$xAxis_or_radius <- 3.2
ppar_a_receptor$yAxis_or_angle <- 2.5
ppar_a_receptor$circle_radius <- 0.7
ppar_a_receptor$text_position <- c(0.5, 0.5)
ppar_a_receptor$draw_me()


ppar_a_receptor <-
  create_oval_node(scaleHeight = 0.8)
ppar_a_receptor$label <- 'PPARa'
ppar_a_receptor$xAxis_or_radius <- 4.8
ppar_a_receptor$yAxis_or_angle <- 2
ppar_a_receptor$circle_radius <- 0.7
ppar_a_receptor$text_position <- c(0.5, 0.5)
ppar_a_receptor$draw_me()

rxr_a_receptor <-
  create_round_rectangular_node(width = 1,
                                height = 0.8,
                                inner_extension_ratio = 0.2)
rxr_a_receptor$label <- 'RXR'
rxr_a_receptor$xAxis_or_radius <- 5
rxr_a_receptor$yAxis_or_angle <- 1.8
rxr_a_receptor$circle_radius <- 0.5
rxr_a_receptor$text_position <- c(0.5, 0.5)
rxr_a_receptor$draw_me()


ppar_y_receptor <-
  create_oval_node(scaleHeight = 0.8)
ppar_y_receptor$label <- 'PPARy'
ppar_y_receptor$xAxis_or_radius <- 6
ppar_y_receptor$yAxis_or_angle <- 2
ppar_y_receptor$circle_radius <- 0.7
ppar_y_receptor$text_position <- c(0.5, 0.5)
ppar_y_receptor$draw_me()

rxr_a_receptor <-
  create_round_rectangular_node(width = 1,
                                height = 0.8,
                                inner_extension_ratio = 0.2)
rxr_a_receptor$label <- 'RXR'
rxr_a_receptor$xAxis_or_radius <- 6.3
rxr_a_receptor$yAxis_or_angle <- 1.8
rxr_a_receptor$circle_radius <- 0.5
rxr_a_receptor$text_position <- c(0.5, 0.5)
rxr_a_receptor$draw_me()




transcriptMachine1 <-
  create_round_rectangular_node(width = 0.5,
                                height = 0.4,
                                inner_extension_ratio = 0.2)
transcriptMachine1$label <- NA
transcriptMachine1$xAxis_or_radius <- 4.3
transcriptMachine1$yAxis_or_angle <- 1.45
transcriptMachine1$circle_radius <- 1
transcriptMachine1$text_position <- c(0.5, 0.5)
transcriptMachine1$draw_me()

transcriptMachine2 <-
  create_round_rectangular_node(width = 0.5,
                                height = 0.4,
                                inner_extension_ratio = 0.2)
transcriptMachine2$label <- NA
transcriptMachine2$xAxis_or_radius <- 5.9
transcriptMachine2$yAxis_or_angle <- 1.45
transcriptMachine2$circle_radius <- 1
transcriptMachine2$text_position <- c(0.5, 0.5)
transcriptMachine2$draw_me()
```


## Last step, add the indicators

```{r}
grid.newpage()

df_lipidsPoints <-
  produce_model_coordinate_points(
    from = -180 ,
    to = 70,
    by = 3,
    radius = 3.5
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5, moveY = 2)

drawer <-
  create_lipidBilayer_drawer(lipidModelIndex = 6, draw_circle_head = T)
drawer$draw_lipid_along_curve(lineX = df_lipidsPoints[1,] , lineY = df_lipidsPoints[2,])

df_nucleus_membrane <-
  produce_model_coordinate_points(
    from = 0,
    to = 360,
    by = 2,
    radius = 2
  ) |> do_scale_affine(scaleHeight = 0.6) |> do_translate_affine(moveX = 5.5, moveY = 1.5)

# drawer <-
#   create_lipidBilayer_drawer(lipidModelIndex = 4, draw_circle_head = T)
# drawer$desired_height <- 0.1
#
#
# startPos <- seq(from = 1, by = 6, to = ncol(df_nucleus_membrane) - 10)
# walk(startPos, .f = function(s){
#   columns <- s:(s+5);
#   drawer$draw_lipid_along_curve(lineX = df_nucleus_membrane[1,columns] , lineY = df_nucleus_membrane[2,columns])
# })
painter2 <- create_roundRectBilayer_drawer(numberOfIntervals = 10)
painter2$desired_height <- 0.08
painter2$draw_along_curve(lineX = df_nucleus_membrane[1,], lineY = df_nucleus_membrane[2,])



drawer_NDA <- create_DNA_drawer(dnaType = 2,numOfRepeats = 3,desired_height = 0.35)
drawer_NDA$draw_me(3.6,1)




Lipoxygenases_receptor <-
  create_round_rectangular_node(width = 0.4,
                                height = 0.6,
                                inner_extension_ratio = 0.2)
Lipoxygenases_receptor$label <- 'Lipoxygenases'
Lipoxygenases_receptor$xAxis_or_radius <- 5
Lipoxygenases_receptor$yAxis_or_angle <- 4
Lipoxygenases_receptor$circle_radius <- 2
Lipoxygenases_receptor$text_position <- c(0.5, 1.1)
Lipoxygenases_receptor$draw_me()




ppar_a_receptor <-
  create_oval_node(scaleHeight = 0.8)
ppar_a_receptor$label <- 'PPARa-1'
ppar_a_receptor$xAxis_or_radius <- 3.2
ppar_a_receptor$yAxis_or_angle <- 2.5
ppar_a_receptor$circle_radius <- 0.7
ppar_a_receptor$text_position <- c(0.5, 0.5)
ppar_a_receptor$draw_me()


ppar_a_receptor <-
  create_oval_node(scaleHeight = 0.8)
ppar_a_receptor$label <- 'PPARa-2'
ppar_a_receptor$xAxis_or_radius <- 4.8
ppar_a_receptor$yAxis_or_angle <- 2
ppar_a_receptor$circle_radius <- 0.7
ppar_a_receptor$text_position <- c(0.5, 0.5)
ppar_a_receptor$draw_me()

rxr_a_receptor <-
  create_round_rectangular_node(width = 1,
                                height = 0.8,
                                inner_extension_ratio = 0.2)
rxr_a_receptor$label <- 'RXR-1'
rxr_a_receptor$xAxis_or_radius <- 5
rxr_a_receptor$yAxis_or_angle <- 1.8
rxr_a_receptor$circle_radius <- 0.5
rxr_a_receptor$text_position <- c(0.5, 0.5)
rxr_a_receptor$draw_me()


ppar_y_receptor <-
  create_oval_node(scaleHeight = 0.8)
ppar_y_receptor$label <- 'PPARy'
ppar_y_receptor$xAxis_or_radius <- 6
ppar_y_receptor$yAxis_or_angle <- 2
ppar_y_receptor$circle_radius <- 0.7
ppar_y_receptor$text_position <- c(0.5, 0.5)
ppar_y_receptor$draw_me()

rxr_a_receptor <-
  create_round_rectangular_node(width = 1,
                                height = 0.8,
                                inner_extension_ratio = 0.2)
rxr_a_receptor$label <- 'RXR-2'
rxr_a_receptor$xAxis_or_radius <- 6.3
rxr_a_receptor$yAxis_or_angle <- 1.8
rxr_a_receptor$circle_radius <- 0.5
rxr_a_receptor$text_position <- c(0.5, 0.5)
rxr_a_receptor$draw_me()




transcriptMachine1 <-
  create_round_rectangular_node(width = 0.5,
                                height = 0.4,
                                inner_extension_ratio = 0.2)
transcriptMachine1$label <- NA
transcriptMachine1$xAxis_or_radius <- 4.3
transcriptMachine1$yAxis_or_angle <- 1.45
transcriptMachine1$circle_radius <- 1
transcriptMachine1$text_position <- c(0.5, 0.5)
transcriptMachine1$draw_me()

transcriptMachine2 <-
  create_round_rectangular_node(width = 0.5,
                                height = 0.4,
                                inner_extension_ratio = 0.2)
transcriptMachine2$label <- NA
transcriptMachine2$xAxis_or_radius <- 5.9
transcriptMachine2$yAxis_or_angle <- 1.45
transcriptMachine2$circle_radius <- 1
transcriptMachine2$text_position <- c(0.5, 0.5)
transcriptMachine2$draw_me()

indicator_drawer <- create_dege_drawer(curvature = -1)
indicator_drawer$draw_me(4.6,1.45,5,1.45)
indicator_drawer$draw_me(6.2,1.45,6.6,1.45)

indicator_drawer$curvature <- 0
indicator_drawer$draw_me(2.5,3.1,2.9,2.7)
indicator_drawer$draw_me(3.5, 2.3, 4.3, 2)
```



# How about the ggplot2 style function called approach


First, let us modeling the elements in the figure. A picture consists of 1. cell membrane, 2. cell nucleus, 3. nodes and 4. edges.

2.1 nuclear envelope
2.2 nuclear DNA

3.1 assembly
3.2 complex
3.3 single protein

4.1 fix node to node indicator
4.2 free location indicator

The relationship could be expressed by the R data structure.
```{r}
model_the_pathway <-
  list(
    cellMembrane = 'cell membrane',
    cellNucleus = list(nuclearEnvelope = 'nuclear envelope', nuclearDNA = 'nuclear DNA'),
    nodes = list(assembly = 'assembly node', complex = 'complex node', singleProtein = 'single protein'),
    edges = list(fix = 'fix node to node indicator', free = 'free location indicator')
  )

lobstr::tree(model_the_pathway)
```



So, the drawing API (Application Programming interface) would be :

```{r eval=FALSE}
pathIllustrator <- membrane(shape = 'ellipse', x = 1, y = 1, w = 3, h = 2) + 
  nuclearEnvelop(x = 2, y = 2, w = 1, h = 1) +  
  nuclearDNA(x = 2.5,y = 2.5, desired_height = 0.3, numOfRepeats = 2) + 
  nodes(data = df1) + 
  edges(fixIndi = df2, freeIndi = df3)
```

And plus the professional graphic elements, we can add some `ggplot2` style features, like `title`.

```{r eval=FALSE}
pathIllustrator <- membrane(shape = 'ellipse', x = 1, y = 1, w = 3, h = 2) + 
  nuclearEnvelop(x = 2, y = 2, w = 1, h = 1) +  
  nuclearDNA(x = 2.5,y = 2.5, h = 0.3, rep = 2)) + 
  nodes(data = df1) + 
  edges(fixIndi = df2, freeIndi = df3) +
  title( "A showcase of the path illustrator", just = 'top')
```

Also, you may need the scale function, to scale the x,y,width and height into the destination size.

## Let us step by step to create the figure 

### The menbrane

```{r}
pathIllustrator <- membrane(shape = 'ellipse', x = 1, y = 1, w = 7, h = 4.2)
pathIllustrator
```

### The nuclearEnvelop

```{r}
pathIllustrator <- nuclearEnvelop(x = 5.5, y = 1.5, w = 4, h = 2.4)
pathIllustrator
```

### Combinate the two cell compounents

```{r}
pathIllustrator <- membrane(shape = 'ellipse', x = 1, y = 0.2, w = 7, h = 4.2) + 
  nuclearEnvelop(x = 3.3, y = 0.5,  w = 4, h = 2.4)
pathIllustrator
```

### and the DNA string

```{r}
pathIllustrator <- membrane(shape = 'ellipse', x = 1, y = 0.2, w = 7, h = 4.2) + 
  nuclearEnvelop(x = 3.3, y = 0.5,  w = 4, h = 2.4) +
  nuclearDNA(x = 3.5, y = 1.5,numOfRepeats = 3)
pathIllustrator
```


### add the node information

```{r}
df <- rbind(
  list('Lipoxygenases',5,4,0.4,0.6,0.2,c(0.5, 1.1), 'roundRect'),
  list(label='PPARa-1',x=3.2,y=2.5,w=1,h=0.8,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='PPARa-2',x=4.8,y=2,w=0.7,h=0.8*0.7,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='RXR-1',x=5,y=1.8,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label='PPARy',x=6,y=2,w=0.7,h=0.8*0.7,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='RXR-2',x=6.3,y=1.8,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label=NA,x=4.3,y=1.45,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label=NA,x=5.9,y=1.45,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect')
)
colnames(df) <- c("label","x","y","width","height","inner_extension_ratio","text_position", "shape")

nodes(data = df)
```

### add the free arrow

```{r}
df <- rbind(
  c(4.6,1.45,5,1.45,-1,0.1),
  c(6.2,1.45,6.6,1.45,-1,0.1),
  c(2.5,3.1,2.9,2.7,-1,0.1),
  c(3.5, 2.3, 4.3, 2,-1,0.1)
)

colnames(df) <- c('x1','y1','x2','y2','curvature','arrowLen')

edges(free_indicator_df = df)

## let us try the pScaleCooordinate
edges(free_indicator_df = df) + pScaleCoord(destWidth = 1, destHeight = 1)
```


## Take all these together as the a whole figure

Now, we could draw a figure like a general `PPAR` pathway with the `ggplot2` style API.

```{r}
df_node <- rbind(
  list('Lipoxygenases',5,4,0.4,0.6,0.2,c(0.5, 1.1), 'roundRect'),
  list(label='PPARa-1',x=3.2,y=2.5,w=1,h=0.8,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='PPARa-2',x=4.8,y=2,w=0.7,h=0.8*0.7,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='RXR-1',x=5,y=1.8,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label='PPARy',x=6,y=2,w=0.7,h=0.8*0.7,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='RXR-2',x=6.3,y=1.8,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label=NA,x=4.3,y=1.45,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label=NA,x=5.9,y=1.45,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect')
)
colnames(df_node) <- c("label","x","y","width","height","inner_extension_ratio","text_position", "shape")

df_freeIndicator <- rbind(
  c(4.6,1.45,5,1.45,-1,0.1),
  c(6.2,1.45,6.6,1.45,-1,0.1),
  c(2.5,3.1,2.9,2.7,-1,0.1),
  c(3.5, 2.3, 4.3, 2,-1,0.1)
)

colnames(df_freeIndicator) <- c('x1','y1','x2','y2','curvature','arrowLen')

pathIllustrator <- membrane(shape = 'ellipse', x = 1, y = 0.2, w = 7, h = 4.2) + 
  nuclearEnvelop(x = 3.3, y = 0.5,  w = 4, h = 2.4) +
  nuclearDNA(x = 3.5, y = 1.5,numOfRepeats = 3) +
  nodes(data = df_node) +
  edges(free_indicator_df = df_freeIndicator) 

pathIllustrator
```


**Not beautifull? we slightly modify the parameters.**

```{r}
df_node <- rbind(
  list('Lipoxygenases',5,4.1,0.4,0.6,0.2,c(0.5, 1.1), 'roundRect'),
  list(label='PPARa-1',x=3,y=2.5,w=1,h=0.8,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='PPARa-2',x=4.4,y=2.2,w=0.7,h=0.8*0.7,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='RXR-1',x=4.4,y=1.8,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label='PPARy',x=5.5,y=2,w=0.7,h=0.8*0.7,ratio=0,tp=c(0.5, 0.5),'ellipse'),
  list(label='RXR-2',x=5.9,y=1.8,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label=NA,x=4.1,y=1.45,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect'),
  list(label=NA,x=5.7,y=1.45,w=0.5,h=0.4,ratio=0.2,tp=c(0.5, 0.5),'roundRect')
)
colnames(df_node) <- c("label","x","y","width","height","inner_extension_ratio","text_position", "shape")

df_freeIndicator <- rbind(
  c(4.6,1.6,5,1.6,1,0.1),
  c(6.2,1.6,6.6,1.6,0,0.1),
  c(2.1, 3.7, 2.9, 3.2,0,0.1),
  c(3.8, 2.3, 4.3, 2,1,0.1)
)

colnames(df_freeIndicator) <- c('x1','y1','x2','y2','curvature','arrowLen')

## You can set the global text font graphics prameters here
set_global_text_pars('fontsize',  9)

pathIllustrator <- membrane(shape = 'roundRect', x = 1, y = 0.2, w = 7, h = 4.2) + 
  nuclearEnvelop(x = 3.3, y = 0.5,  w = 4, h = 2.4) +
  nuclearDNA(x = 3.5, y = 1.3,numOfRepeats = 3) +
  nodes(data = df_node) +
  edges(free_indicator_df = df_freeIndicator)  + 
  pTitle(name = "An approximate way to visulize the PPAR pathway.", gpar(fontface = 'bold'))

pathIllustrator
```

