---
title: "stepByStep_toDraw_WntSignalingPathway"
output: rmarkdown::html_vignette
number_sections: true
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
vignette: >
  %\VignetteIndexEntry{stepByStep_toDraw_WntSignalingPathway}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=7, fig.height=5,
  fig.align = "center"
)
```


I frequently use the `grid` and `purrr` package, so besides load the `PathwayIlluminator`, these two packages are needed.

```{r setup}
library(PathwayIlluminator)
library(grid)
library(purrr)
## new packages need to added
library(gridBezier)
```


## First, the basic self-contained bio graphics model

The following codes can display the supported models.

```{r}
basic_bioGraphics_templates |> names()
```

Draw a FZD protein:

```{r fig.height=3,fig.width=4}
location_of_fzd <- create_point(1.5,2)
fzdProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'FZD_1')
fzdProt$xAxis_or_radius <- location_of_fzd@x
fzdProt$yAxis_or_angle <- location_of_fzd@y
fzdProt$circle_radius <- 1
fzdProt$gpar_shape <- gpar(fill = 'brown')
fzdProt$label <- "FZD"
fzdProt$text_position <- c(0.5,0)
fzdProt$draw_me()
```


## draw a basic WNT signaling off state pathway

Let us draw a basic off state Wnt pathway.

```{r}
grid.newpage()
show_grid_forAssistance()
clear_global_bioGraphics_nodes_list()

painter <- create_lipidBilayer_drawer(draw_circle_head = F)
# painter$lipid_head_par <- gpar(fill = 'lightblue', col = 'NA')
painter$percentage_of_off_track <- 0.1
painter$desired_height <- 0.15

coords <- create_round_rectangle_xyCoords(x = 1, y = 0.5, w = 3, h = 3, r = 1, space = 0.1)


painter$draw_lipid_along_curve(lineX = coords[1, ],  lineY = coords[2, ] , closedPolygon = T)



location_of_lrp <- create_point(coords[1,1], coords[2,1])
lrpProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'LRP_2')
lrpProt$xAxis_or_radius <- location_of_lrp@x
lrpProt$yAxis_or_angle <- location_of_lrp@y
lrpProt$circle_radius <- 0.15
lrpProt$gpar_shape <- gpar(fill = 'white')
lrpProt$label <- "LRP"
lrpProt$text_position <- c(0.5,0)
lrpProt$draw_me()

location_of_fzd <- create_point(coords[1,11], coords[2,11])
fzdProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'FZD_1')
fzdProt$xAxis_or_radius <- location_of_fzd@x
fzdProt$yAxis_or_angle <- location_of_fzd@y
fzdProt$circle_radius <- 1
fzdProt$gpar_shape <- gpar(fill = 'brown')
fzdProt$label <- "FZD"
fzdProt$text_position <- c(0.5,0)
fzdProt$draw_me()


location_of_axin <- create_point(2, 2.5)
axinProt <- create_rectangular_node(scaleHeight = 0.5,inner_extension_ratio = 0.15)
axinProt$xAxis_or_radius <- location_of_axin@x
axinProt$yAxis_or_angle <- location_of_axin@y
axinProt$circle_radius <- 0.8
axinProt$gpar_shape <- gpar(fill = 'green4')
axinProt$label <- "AXIN"
axinProt$text_position <- c(0.5,0.5)
axinProt$draw_me()

location_of_apc <- create_point(1.8, 2.1)
apcProt <- create_oval_node(scaleHeight = 0.6, inner_extension_ratio = 0.15)
apcProt$xAxis_or_radius <- location_of_apc@x
apcProt$yAxis_or_angle <- location_of_apc@y
apcProt$circle_radius <- 0.4
apcProt$gpar_shape <- gpar(fill = 'lightblue')
apcProt$label <- "APC"
apcProt$text_position <- c(0.5,0.5)
apcProt$draw_me()

location_of_gsk3b <- create_point(2.5, 2.2)
gsk3bProt <- create_oval_node(scaleHeight = 0.6, inner_extension_ratio = 0.15)
gsk3bProt$xAxis_or_radius <- location_of_gsk3b@x
gsk3bProt$yAxis_or_angle <- location_of_gsk3b@y
gsk3bProt$circle_radius <- 0.4
gsk3bProt$gpar_shape <- gpar(fill = 'orange4')
gsk3bProt$label <- "GSK3B"
gsk3bProt$text_position <- c(0.5,0.5)
gsk3bProt$draw_me()

location_of_ck1a <- create_point(2.2, 1.8)
ck1aProt <- create_oval_node(scaleHeight = 0.5, inner_extension_ratio = 0.15)
ck1aProt$xAxis_or_radius <- location_of_ck1a@x
ck1aProt$yAxis_or_angle <- location_of_ck1a@y
ck1aProt$circle_radius <- 0.4
ck1aProt$gpar_shape <- gpar(fill = 'pink1')
ck1aProt$label <- "CK1A"
ck1aProt$text_position <- c(0.5,0.5)
ck1aProt$draw_me()


bCatProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'bCatenin')
bCatProt$xAxis_or_radius <- 2.5
bCatProt$yAxis_or_angle <- 1
bCatProt$circle_radius <- 1
bCatProt$gpar_shape <- gpar(fill = 'white')
bCatProt$label <- "B-CATENIN"
bCatProt$text_position <- c(0.5,0.5)
bCatProt$gpar_shape <- gpar(fill = 'purple1')
bCatProt$draw_me()

bCatProt2 <-
  create_selfContained_simple_bioGraphicsNode(name = 'bCatenin')
bCatProt2$xAxis_or_radius <- 3.3
bCatProt2$yAxis_or_angle <- 1.5
bCatProt2$circle_radius <- 1
bCatProt2$rotation_angle_inRadian <- 30 * ONE_DEGREE_IN_RADIAN
bCatProt2$gpar_shape <- gpar(fill = 'grey90')
bCatProt2$label <- "B-CAT-Phos"
bCatProt2$text_position <- c(0.5,0.5)
bCatProt2$draw_me()

nodeList <- get_global_bioGraphics_nodes_list()
nodeList |> names()

node1 <- nodeList[['B-CATENIN']]
node2 <- nodeList[['B-CAT-Phos']]
node1_grob <- node1$grob
node2_grob <- node2$grob
x1 <- node1$x;x2 <-  node2$x
y1 <- node1$y;y2 <-  node2$y

arrow <- arrow(type = 'closed', length = unit(0.1, 'in'))
draw_lineArrow_accordingTo_grobAndPoints(node1_grob,node2_grob,x1,y1,x2,y2,arrow = arrow)

```


Remove the assistant grid lines are the desired figure.


```{r echo=FALSE}
grid.newpage()
clear_global_bioGraphics_nodes_list()

painter <- create_lipidBilayer_drawer(draw_circle_head = F)
# painter$lipid_head_par <- gpar(fill = 'lightblue', col = 'NA')
painter$percentage_of_off_track <- 0.1
painter$desired_height <- 0.15

coords <- create_round_rectangle_xyCoords(x = 1, y = 0.5, w = 3, h = 3, r = 1, space = 0.1)


painter$draw_lipid_along_curve(lineX = coords[1, ],  lineY = coords[2, ] , closedPolygon = T)



location_of_lrp <- create_point(coords[1,1], coords[2,1])
lrpProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'LRP_2')
lrpProt$xAxis_or_radius <- location_of_lrp@x
lrpProt$yAxis_or_angle <- location_of_lrp@y
lrpProt$circle_radius <- 0.15
lrpProt$gpar_shape <- gpar(fill = 'white')
lrpProt$label <- "LRP"
lrpProt$text_position <- c(0.5,0)
lrpProt$draw_me()

location_of_fzd <- create_point(coords[1,11], coords[2,11])
fzdProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'FZD_1')
fzdProt$xAxis_or_radius <- location_of_fzd@x
fzdProt$yAxis_or_angle <- location_of_fzd@y
fzdProt$circle_radius <- 1
fzdProt$gpar_shape <- gpar(fill = 'brown')
fzdProt$label <- "FZD"
fzdProt$text_position <- c(0.5,0)
fzdProt$draw_me()


location_of_axin <- create_point(2, 2.5)
axinProt <- create_rectangular_node(scaleHeight = 0.5,inner_extension_ratio = 0.15)
axinProt$xAxis_or_radius <- location_of_axin@x
axinProt$yAxis_or_angle <- location_of_axin@y
axinProt$circle_radius <- 0.8
axinProt$gpar_shape <- gpar(fill = 'green4')
axinProt$label <- "AXIN"
axinProt$text_position <- c(0.5,0.5)
axinProt$draw_me()

location_of_apc <- create_point(1.8, 2.1)
apcProt <- create_oval_node(scaleHeight = 0.6, inner_extension_ratio = 0.15)
apcProt$xAxis_or_radius <- location_of_apc@x
apcProt$yAxis_or_angle <- location_of_apc@y
apcProt$circle_radius <- 0.4
apcProt$gpar_shape <- gpar(fill = 'lightblue')
apcProt$label <- "APC"
apcProt$text_position <- c(0.5,0.5)
apcProt$draw_me()

location_of_gsk3b <- create_point(2.5, 2.2)
gsk3bProt <- create_oval_node(scaleHeight = 0.6, inner_extension_ratio = 0.15)
gsk3bProt$xAxis_or_radius <- location_of_gsk3b@x
gsk3bProt$yAxis_or_angle <- location_of_gsk3b@y
gsk3bProt$circle_radius <- 0.4
gsk3bProt$gpar_shape <- gpar(fill = 'orange4')
gsk3bProt$label <- "GSK3B"
gsk3bProt$text_position <- c(0.5,0.5)
gsk3bProt$draw_me()

location_of_ck1a <- create_point(2.2, 1.8)
ck1aProt <- create_oval_node(scaleHeight = 0.5, inner_extension_ratio = 0.15)
ck1aProt$xAxis_or_radius <- location_of_ck1a@x
ck1aProt$yAxis_or_angle <- location_of_ck1a@y
ck1aProt$circle_radius <- 0.4
ck1aProt$gpar_shape <- gpar(fill = 'pink1')
ck1aProt$label <- "CK1A"
ck1aProt$text_position <- c(0.5,0.5)
ck1aProt$draw_me()


bCatProt <-
  create_selfContained_simple_bioGraphicsNode(name = 'bCatenin')
bCatProt$xAxis_or_radius <- 2.5
bCatProt$yAxis_or_angle <- 1
bCatProt$circle_radius <- 1
bCatProt$gpar_shape <- gpar(fill = 'white')
bCatProt$label <- "B-CATENIN"
bCatProt$text_position <- c(0.5,0.5)
bCatProt$gpar_shape <- gpar(fill = 'purple1')
bCatProt$draw_me()

bCatProt2 <-
  create_selfContained_simple_bioGraphicsNode(name = 'bCatenin')
bCatProt2$xAxis_or_radius <- 3.3
bCatProt2$yAxis_or_angle <- 1.5
bCatProt2$circle_radius <- 1
bCatProt2$rotation_angle_inRadian <- 30 * ONE_DEGREE_IN_RADIAN
bCatProt2$gpar_shape <- gpar(fill = 'grey90')
bCatProt2$label <- "B-CAT-Phos"
bCatProt2$text_position <- c(0.5,0.5)
bCatProt2$draw_me()

nodeList <- get_global_bioGraphics_nodes_list()
nodeList |> names()

node1 <- nodeList[['B-CATENIN']]
node2 <- nodeList[['B-CAT-Phos']]
node1_grob <- node1$grob
node2_grob <- node2$grob
x1 <- node1$x;x2 <-  node2$x
y1 <- node1$y;y2 <-  node2$y

arrow <- arrow(type = 'closed', length = unit(0.1, 'in'))
draw_lineArrow_accordingTo_grobAndPoints(node1_grob,node2_grob,x1,y1,x2,y2,arrow = arrow)

```
